Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-14 paper/introduction.tex
Minor intro fixes, plus minor related work fixes.

First, we learn a classifier for split errors with a convolutional neural network (CNN). This takes as input patches of membrane segmentation probabilities, cell segmentation masks, and boundary masks, and outputs a probabiltiy score. As we must process large data, this classifier only operates on the boundaries between cells, which reduces computation over methods which analyze every pixel. For merge errors, we invert and reuse the split classification network, instead asking it to rate a series of generated candidate boundaries which hypothesize a split. We compute corrections for both types of errors.

Second, we propose a greedy algorithm for guided proofreading. Possible erroneous regions are sorted by their score, and a correction is generated for each region. Then, a user works through this list of regions and corrections. In a forced choice setting, the user either selects a correction or skips it to advance to the next region. In an automatic setting, errors with a high probability can be automatically corrected first, given an appropriate probability threshold, after which the user would take over. Finally, to test the limits of performance, we create an oracle with ground truth knowledge, who accepts corrections only when they improve the segmentation. This equals perfect proofreading.

>>>>

First, we learn a classifier for split errors with a convolutional neural network (CNN). This takes as input patches of membrane segmentation probabilities, cell segmentation masks, and boundary masks, and outputs a probabiltiy score. As we must process large data, this classifier only operates on cell boundaries, which reduces computation over methods which analyze every pixel. For merge errors, we invert and reuse the split classification network, instead asking it to rate a set of generated candidate boundaries which hypothesize a split. We compute corrections for both types of errors.

Second, we propose a greedy algorithm for guided proofreading. Possible erroneous regions are sorted by their score, and a correction is generated for each region. Then, a user works through this list of regions and corrections. In a forced choice setting, the user either selects a correction or skips it to advance to the next region. In an automatic setting, errors with a high probability can be automatically corrected first, given an appropriate probability threshold, after which the user would take over. Finally, to test the limits of performance, we create an oracle with knowledge of the ground truth, which only accepts corrections when they improve the segmentation. This equals perfect proofreading.

### 2016-11-14 paper/related_work.tex
Update intro, rel. work and methods.
Minor intro fixes, plus minor related work fixes.

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/architecture.png}
\end{center}
  \vspace{-4mm}
   \caption{We build the guided proofreading classifiers using a traditional CNN architecture. The network is based on four convolutional layers, each followed by max pooling as well as dropout regularization. The 4-channel input patches are rated as either correct splits or as split errors.}
\label{fig:architecture}
\end{figure*}

@@

Many works tackle this problem. NeuroProof \cite{neuroproof2013} decreases error rates by learning a agglomeration on over-segmentations of images, based on a random forest classifier. Vazquez-Reina \etal~\cite{amelio_segmentation} take whole EM volumes into account rather than a per section approach, then solve a fusion problem with a global context. Kaynig \etal~\cite{kaynig10} propose a random forest classifier coupled with an anisotropic smoothing prior in a conditional random field framework with 3D segment fusion. Bogovic \etal~\cite{BogovicHJ13} learn 3D features unsupervised, and show that they can be better than by-hand designs.

@@

All these approaches make good progress; however, in general, proofreading is still required to correct errors.

%Inspired by Bogovic \etal, we extend their features for our guided proofreading classifiers (Section \ref{sec:methods}).

\textbf{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments. One expert tool is Raveler, introduced by Chklovskii~\etal~\cite{chklovskii2010, raveler}. Raveler is used today by professional proofreaders, and it offers many parameters for tweaking the process. Similar systems exist as products or plugins to visualization systems,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}.

@@

All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of the time~\cite{proofreading_bottleneck,haehn_dojo_2014}. Recent works propose computer-aided proofreading systems which help reduce the time spent in this visual search task.

%Most relevant methods here use heuristics to analyze the image data to find potential errors. 
\textbf{Computer-aided Proofreading.} Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This segmentation technique produces uncertainty estimates, which can be used to present potential regions for proofreading to the user. While it works on isotropic volumes, more work is needed to apply it to anisotropic volumes, like most connectomics datasets.

>>>>

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/architecture.pdf}
\end{center}
  \vspace{-4mm}
   \caption{We build the guided proofreading classifiers using a traditional CNN architecture. The network is based on four convolutional layers, each followed by max pooling as well as dropout regularization. The 4-channel input patches are rated as either correct splits or as split errors.}
\label{fig:architecture}
\end{figure*}

@@

Many works tackle this problem. NeuroProof \cite{neuroproof2013} decreases error rates by learning a agglomeration on over-segmentations of images, based on a random forest classifier. Vazquez-Reina \etal~\cite{amelio_segmentation} consider whole EM volumes rather than a per section approach, then solve a fusion problem with a global context. Kaynig \etal~\cite{kaynig10} propose a random forest classifier coupled with an anisotropic smoothing prior in a conditional random field framework with 3D segment fusion. Bogovic \etal~\cite{BogovicHJ13} learn 3D features unsupervised, and show that they can be better than by-hand designs.

@@

All these approaches make good progress; however, in general, proofreading is still required to correct errors.
\\~\\
\textbf{Interactive Proofreading.} While proofreading is very time consuming, it is fairly easy for humans to perform corrections through splitting and merging segments. One expert tool is Raveler, introduced by Chklovskii~\etal~\cite{chklovskii2010, raveler}. Raveler is used today by professional proofreaders, and it offers many parameters for tweaking the process. Similar systems exist as products or plugins to visualization systems,~\eg V3D~\cite{proofreading_bottleneck} or AVIZO~\cite{markus_proofreading}.

@@

All interactive proofreading solutions require the user to find potential errors manually, which takes the majority of the time~\cite{proofreading_bottleneck,haehn_dojo_2014}. Recent works propose computer-aided proofreading systems which help reduce the time spent in this visual search task.
\\~\\
\textbf{Computer-aided Proofreading.} Uzunbas \etal showed that potential labeling errors can be found by considering the merge tree of an automatic segmentation method~\cite{uzunbas}. The authors track uncertainty throughout the automatic labeling by training a conditional random field. This segmentation technique produces uncertainty estimates, which inform potential regions for proofreading to the user. While this applies to isotropic volumes, more work is needed to apply it to anisotropic volumes, like most connectomics datasets.
